First paper - Draft

### 2017-06-02 paper/paper.Rnw
Ran paper with code - all working

<<packages_conf, echo = F>>=
  library(arm)
  library(saves)
  library(haven)
  library(PISA2000lite)
  library(PISA2003lite)
  library(PISA2006lite)
  library(PISA2009lite)
  library(PISA2012lite)
  library(intsvy)
  library(cimentadaj) # For pisa_countrynames
  library(countrycode) # For region variable
  library(tidyverse)
  library(car)
  library(readr)
  library(SAScii)
  library(inequalityintsvy)
  library(lme4)
  library(modelr)

@@

<<loading_data/recoding, echo = F, cache = TRUE>>=
pisa_all <- read_rds("./data/pisa_listcol.Rdata")
pisa_all2 <- pisa_all

@@

<<escs_trend, echo = F, cache = TRUE>>=
  # Rescaled trend ESCS data to merge.
  # This only has data for seq(2000, 2012, 3) because
  # PISA 2015 has the ESCS trend variable.
  dir <- tempdir()
  file_name <- "escs_trend.zip"
  download.file("http://vs-web-fs-1.oecd.org/pisa/trend_escs_SPSS.zip",
                destfile = file.path(dir, file_name))
  unzip(file.path(dir, file_name), exdir = dir)
  escs_trend <- map(file.path(dir, list.files(dir, pattern = ".sav")), haven::read_spss)
  file.remove(file.path(dir, list.files(dir)))

@@

<<merge_escs_pisa, echo = F, cache = TRUE>>=
   # Next we'll merge the ESCS data with the PISA data. As explained above, the 6th data (PISA
  # 2015) doesn't need to be merged so I exclude it with this vector
  exclude <- -6

@@

<<functions_for_modelling, echo = F>>=

@@

<<modelling, echo = F, cache = T>>=
adapted_year_data <-
    map(pisa_all2$value, ~ {
      if (unique(.x$wave) == "pisa2000") {
        # pisa2000 has a different coding so here I recode 6 to 7 so that in all waves the top edu
        # is 7 and the bottom is 1
        .x <- 
          mutate(.x, new_hisced = as.character(dplyr::recode(as.numeric(high_edu_broad), `6` = 7)))
      } else {
        .x <-
          mutate(.x, new_hisced = as.character(high_edu_broad))
      }
      .x
})

@@

<<ci_for_difference, echo = F>>=
reduced_data <-
    map2(results_math, years, function(.x, .y) {
      .x %>%
        mutate(wave = .y) %>%
        filter(!is.na(escs_dummy))
    }) %>%
    bind_rows() %>%
    mutate(lower = Mean - 1.96 * s.e.,
           upper = Mean + 1.96 * s.e.)
@

<<graphin differences>>=
  reduced_data %>%
    filter(country %in% c("United States")) %>%
    ggplot(aes(as.character(wave), Mean, group = escs_dummy, colour = escs_dummy)) +
    geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
    geom_line() +
    facet_wrap(~ country)
@

@@

<<>>=

@@

@@

Try one!
\end{document}

>>>>

<<working directory, echo = F>>=
opts_knit$set(root.dir = '..')

opts_chunk$set(echo = F,
               message = F,
               warning = F,
               include = F,
               cache.lazy = F,
               results = 'asis')
@

<<packages_conf, echo = F>>=
  library(knitr)
  library(arm)
  library(saves)
  library(haven)
  library(PISA2000lite)
  library(PISA2003lite)
  library(PISA2006lite)
  library(PISA2009lite)
  library(PISA2012lite)
  library(intsvy)
  library(cimentadaj) # For pisa_countrynames
  library(countrycode) # For region variable
  library(car)
  library(readr)
  library(SAScii)
  library(inequalityintsvy)
  library(lme4)
  library(modelr)
  library(tidyverse)

@@

<<loading_data-recoding, cache = TRUE>>=
pisa_all <- read_rds("./data/pisa_listcol.Rdata")
pisa_all2 <- pisa_all

@@

<<escs_trend, cache = TRUE>>=
  # Rescaled trend ESCS data to merge.
  # This only has data for seq(2000, 2012, 3) because
  # PISA 2015 has the ESCS trend variable.
  dir <- tempdir()
  file_name <- "escs_trend.zip"
  download.file("http://vs-web-fs-1.oecd.org/pisa/trend_escs_SPSS.zip",
                destfile = file.path(dir, file_name))
  unzip(file.path(dir, file_name), exdir = dir)
  escs_trend <- map(file.path(dir, list.files(dir, pattern = ".sav")), haven::read_spss)
  file.remove(file.path(dir, list.files(dir)))

@@

<<merge_escs_pisa, cache = TRUE>>=
   # Next we'll merge the ESCS data with the PISA data. As explained above, the 6th data (PISA
  # 2015) doesn't need to be merged so I exclude it with this vector
  exclude <- -6

@@

<<functions_for_modelling>>=

@@

<<modeling, cache = T>>=
adapted_year_data <-
    map(pisa_all2$value, ~ {
      if (unique(.x$wave) == "pisa2000") {
        # pisa2000 has a different coding so here I recode 6 to 7 so that in all waves the top edu
        # is 7 and the bottom is 1
        .x <- 
          mutate(.x, new_hisced = as.character(dplyr::recode(as.numeric(high_edu_broad), `6` = 7)))
      } else {
        .x <-
          mutate(.x, new_hisced = as.character(high_edu_broad))
      }
      .x
})

@@

<<ci_for_difference>>=
reduced_data <-
    map2(results_math, years, function(.x, .y) {
      .x %>%
        mutate(wave = .y) %>%
        filter(!is.na(escs_dummy))
    }) %>%
    bind_rows() %>%
    mutate(lower = Mean - 1.96 * s.e.,
           upper = Mean + 1.96 * s.e.)
@

<<graphin differences, include = T, out.height = '5in', out.width = '5.5in', fig.align = 'center'>>=
  reduced_data %>%
    filter(country %in% c("United States")) %>%
    ggplot(aes(as.character(wave), Mean, group = escs_dummy, colour = escs_dummy)) +
    geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
    geom_line() +
    facet_wrap(~ country)
@

@@

<<include = T, out.height = '5in', out.width = '5.5in', fig.align = 'center'>>=

@@

# The gap between the top 90th and the 50th, did it grow?
# The gap between the top 50th and the 10th, did it grow?

# A weak welfare system, together with income inequality, what's their pattern?
# What if we put the school differentiation/tracking aspect in? Are there country groups based on these
# patterns.

# Show that within top and bottom educated categories, there is reasonable variation of SES index (to justify that your approach of suing the top and bottom percentiles within each category is the right approach)

# In countries where there is high differentiation/tracking, is there a jump in the evolution of the gap between PIRLS/TIMSS and PISA?

@@

Recent research on educational inequality has found that differences in test peformance between High-SES and Low-SES kids has been growing quickly over the years. The vast literature on educational inequality has mainly concentrated on the United States (reardon here). First, because it is the only country where cognitive testing is very widespread across surveys. And secondly, this trend has allowed to have testing records as early as 1940 (check reardon) until present day. Using this information, Reardon (2011) is the first to investigate the evolution of the cognitive gap and the results are very surprising. Not only has the cognitive gap between the 90th income percentile and the 10th income percentile grown over time, but it has grown faster and to be wider than the highly contested white-black gap (cite study of white-black gap).

The widening of the achievement gap has been happening in parallel to the growth of income inequality. Although very suggestive, it is hard to link both things causally. The downside of this research study is that it is mainly US-based, and not a lot of evidence is available in an international context. To the best of my knowledge, the only attempt to take this to an international context is the work by Chmielewski and Reardon (2016). They find that there is considerable variation in the achievement gap between top and bottom earning families. However, their design is quite different from the one from Reardon (2011). Reardon (2011) takes studies in the U.S starting from the 1940's until 2015 \footnote{Each study is independent of each other meaning that the it might've been given to 6 year olds as well as to 12 year olds. Although the author adjusts for age, the trends can't be generalized to age-specific, but rather in overall terms.} and makes them comparable across time. That is, he builds a trend of achievement gap. Chmielewski and Reardon (2016) use the international surveys PISA and PIRLS to compare the achievement gap across countries. Unfortunately, very few countries can be compared across time in PISA.

This paper introduces one novelty in the literature which is to evaluate the evolution of the High/Low SES achievement gap in the past 15 years for all PISA participant countries. This is different from previous work because it concentrates solely on 15 year old children, and it attempts to capture the evolution of the achievement gap for each country.

Do we need to distinguish between age-group achievement gaps?

\end{document}

### 2017-06-02 paper/paper.tex
Ran paper with code - all working

\documentclass[11pt, a4paper]{article}
\bibliographystyle{apalike}
\pagestyle{headings}

@@

\title{First paper - Draft}
\author{Jorge Cimentada}

\begin{document}
\setlength{\parindent}{2em}
\setlength{\parskip}{1em}
\showboxdepth=5
\showboxbreadth=5

@@

<<working directory, echo = F>>=
opts_knit$set(root.dir = '..')

opts_chunk$set(echo = F,
               message = F,
               warning = F,
               include = F,
               cache.lazy = F,
               results = 'asis')
@

<<packages_conf, echo = F>>=
  library(knitr)
  library(arm)
  library(saves)
  library(haven)
  library(PISA2000lite)
  library(PISA2003lite)
  library(PISA2006lite)
  library(PISA2009lite)
  library(PISA2012lite)
  library(intsvy)
  library(cimentadaj) # For pisa_countrynames
  library(countrycode) # For region variable
  library(car)
  library(readr)
  library(SAScii)
  library(inequalityintsvy)
  library(lme4)
  library(modelr)
  library(tidyverse)

  # source("./transform_data.R")

  # Conf for PISA_2015
  pisa2015_conf <- list(variables = list(pvlabelpref = "PV",
                                         pvlabelsuff = "READ",
                                         weightFinal = "W_FSTUWT",
                                         weightBRR = "W_FSTURWT"),
          parameters = list(cutoffs = c(357.77, 420.07, 482.38, 544.68, 606.99, 669.30),
                                          percentiles = c(5, 10, 25, 75, 90, 95),
                                          PVreps = 10,
                                          BRRreps = 80,
                                          weights = "BRR",
                                          replication_scheme = 'pisa')
  )

@

@@

<<loading_data-recoding, cache = TRUE>>=
pisa_all <- read_rds("./data/pisa_listcol.Rdata")
pisa_all2 <- pisa_all

years <- seq(2000, 2015, 3)
countries <- c("Germany", "United States", "Denmark", "Sweden", "United Kingdom",
                 "Spain", "Italy", "Canada", "Australia")

db <- paste0("pisa", years)
pisa_all2$value <- map2(pisa_all2$value, db, ~ { .x$wave <- .y; .x})
pisa_all2$value[[1]]$CNT <- pisa_all2$value[[1]]$COUNTRY

pisa_all2$value <- map(pisa_all2$value, ~ {
  .x$father_edu <- car::recode(as.numeric(.x$FISCED), "8:9 = NA")
  .x$mother_edu <- car::recode(as.numeric(.x$MISCED), "8:9 = NA")
  .x$high_edu_broad <- pmax(.x$father_edu, .x$mother_edu)
  .x$country <- pisa_countrynames[as.character(.x$CNT)]

  if (any(unique(.x$wave) %in% c("pisa2012", "pisa2015"))) {
    .x$father_edu <- .x$father_edu + 1
    .x$mother_edu <- .x$mother_edu + 1
    .x$high_edu_broad <- .x$high_edu_broad + 1
  }
  .x
})

reliability_pisa <-
  c("2000" = 0.81,
    "2003" = 0.85,
    "2006" = 0.78,
    "2009" = 0.74,
    "2012" = 0.82,
    "2015" = 0.74) # 2015 imputed

@

<<escs_trend, cache = TRUE>>=
  # Rescaled trend ESCS data to merge.
  # This only has data for seq(2000, 2012, 3) because
  # PISA 2015 has the ESCS trend variable.
  dir <- tempdir()
  file_name <- "escs_trend.zip"
  download.file("http://vs-web-fs-1.oecd.org/pisa/trend_escs_SPSS.zip",
                destfile = file.path(dir, file_name))
  unzip(file.path(dir, file_name), exdir = dir)
  escs_trend <- map(file.path(dir, list.files(dir, pattern = ".sav")), haven::read_spss)
  file.remove(file.path(dir, list.files(dir)))

  escs_trend <-
    map(escs_trend, ~ {
    mutate(.x, cnt = pisa_countrynames[cnt]) %>%
    rename(country = cnt)
  })

@

<<merge_escs_pisa, cache = TRUE>>=
   # Next we'll merge the ESCS data with the PISA data. As explained above, the 6th data (PISA
  # 2015) doesn't need to be merged so I exclude it with this vector
  exclude <- -6

  # Loop in parallel to the PISA data, the ESCS data and the year vector (which is seq(2012, 2015, 3))
  pisa_all2$value[exclude] <-
    pmap(list(pisa_all2$value[exclude], escs_trend, years[exclude]), function(.x, .y, .z) {

    # The escs data needs to have the key variables the same class as the
    # same data.
    escs <-
      .y %>% mutate(schoolid = as.numeric(schoolid),
                    stidstd = as.numeric(stidstd))

    # .z is the corresponding year that will be created as a column
    # And perform the same transformation of the key variables as in the ESCS data
    data_trend <-
      .x %>%
        mutate(
          year = .z,
          schoolid = as.numeric(as.character(SCHOOLID)),
          stidstd = as.numeric(as.character(STIDSTD))
          ) %>%
   left_join(escs,
              by = c("country", "schoolid", "stidstd"))

    message(paste(unique(.x$wave), "done"))

    data_trend
  })

  pisa_all2$value[[6]] <-
    pisa_all2$value[[6]] %>%
    rename(escs_trend = ESCS)
@

<<functions_for_modelling>>=

# Function calculates the bottom 30th quantile for the bottom educated and the 70th quantile
# for the top educated. If the quantiles can't be estimated, it returns two NA's instead
quantile_missing <- function(df, weights) {

    df_lower <- filter(df, new_hisced == 1)
    df_upper <- filter(df, new_hisced == 7)

    quan_lower <- try(Hmisc::wtd.quantile(df_lower$escs_trend,
                                          weights = df_lower[[weights]],
                                          probs = c(0.30)))

    quan_upper <- try(Hmisc::wtd.quantile(df_upper$escs_trend,
                                    weights = df_upper[[weights]],
                                    probs = c(0.70)))

    if (any("try-error" %in% c(class(quan_lower), class(quan_upper)))) {
      return(c(NA, NA))
      } else {
     return(c(quan_lower[1], quan_upper[1]))
    }
}

# Producing the plot to get the difference between the top 30% of the high educated
# vs the bottom 30% of the low educated. This function loops through each dataset/country
# and survey reliability and estimates the difference while also extracting the s.e. of each
# difference.

# It returns a dataframe for each survey with all countries and respective coefficients and
# standard errors.
test_diff <- function(df, reliability, test) {

    map2(df, reliability, function(.x, .y) {

      conf <- if (unique(.x$wave) == "pisa2015") pisa2015_conf else pisa_conf
      weights_var <- conf$variables$weightFinal

      country_split <- split(.x, .x$country)

      country_list <- map(country_split, function(country) {
        print(unique(country$country))

        # In some countries the quan can't be estimated because of very few obs.
        # The function doesn't stop but returns two NA's.
        quan <- quantile_missing(country, weights_var)

        # It's very important to create a variable that returns the number of observations of this dummy
        # For each country. Possibly to weight by the number of observations.
        country$escs_dummy <-
          with(country, case_when(escs_trend >= quan[2] ~ 1,
                                  escs_trend <= quan[1] ~ 0))
        country
      })

      .x <-
        enframe(country_list) %>%
        unnest(value)

      .x <-
        .x %>%
        select(wave, matches(paste0("^PV.*", test, "$")), escs_dummy,
               country, one_of(weights_var),
               AGE)

      message(paste(unique(.x$wave), "data ready"))

      test_vars <- paste0("PV", seq_len(conf$parameters$PVreps), test)
      .x[test_vars] <- map(.x[test_vars], ~ ifelse(.x == 9997, NA, .x))

      # Calculate median math score of all PV's
      .x$dv <- apply(.x[test_vars], 1, median, na.rm = T)

      # Should I estimate the model separately by country?
      mod1 <- lm(dv ~ AGE,
                 weights = .x[[weights_var]],
                 data = .x,
                 na.action = "na.exclude")

      # Take residuals of model and divide by rmse. Multiply that by
      # 1 / sqrt(reliability of each survey), which is .y in the loop.
      .x$adj_pvnum <- resid(mod1)/rmse(mod1, .x) * 1 / sqrt(.y)

      mod2 <-
        lmer(adj_pvnum ~ escs_dummy + (1 + escs_dummy | country),
             data = .x,
             weights = .x[[weights_var]])

      # Take the country coefficients (absolute coefficients)
      country_coef <-
        coef(mod2)$country %>%
        rownames_to_column() %>%
        gather(escs_dummy, Mean, -rowname) %>%
        mutate(escs_dummy = dplyr::recode(escs_dummy,
                                          `(Intercept)` = "0",
                                          `escs_dummy` = "1"))

      # Take the absolute country standard errors
      se <-
        se.coef(mod2)$country %>%
        as.data.frame() %>%
        rownames_to_column() %>%
        gather(escs_dummy, s.e., -rowname) %>%
        mutate(escs_dummy = dplyr::recode(escs_dummy,
                                          `(Intercept)` = "0",
                                          `escs_dummy` = "1"))

      results <-
        inner_join(country_coef, se, by = c("rowname", "escs_dummy")) %>%
        rename(country = rowname) %>%
        arrange(country, escs_dummy)

      message(paste0(unique(.x$wave), " modeling done"))
      results
    })
}
@

<<modeling, cache = T>>=
adapted_year_data <-
    map(pisa_all2$value, ~ {
      if (unique(.x$wave) == "pisa2000") {
        # pisa2000 has a different coding so here I recode 6 to 7 so that in all waves the top edu
        # is 7 and the bottom is 1
        .x <- 
          mutate(.x, new_hisced = as.character(dplyr::recode(as.numeric(high_edu_broad), `6` = 7)))
      } else {
        .x <-
          mutate(.x, new_hisced = as.character(high_edu_broad))
      }
      .x
})

results_math <- test_diff(adapted_year_data, reliability_pisa, "MATH")
results_read <- test_diff(adapted_year_data, reliability_pisa, "READ")
# US is missing for reading
@

<<ci_for_difference>>=
reduced_data <-
    map2(results_math, years, function(.x, .y) {
      .x %>%
        mutate(wave = .y) %>%
        filter(!is.na(escs_dummy))
    }) %>%
    bind_rows() %>%
    mutate(lower = Mean - 1.96 * s.e.,
           upper = Mean + 1.96 * s.e.)
@

<<graphin differences, include = T, out.height = '5in', out.width = '5.5in', fig.align = 'center'>>=
  reduced_data %>%
    filter(country %in% c("United States")) %>%
    ggplot(aes(as.character(wave), Mean, group = escs_dummy, colour = escs_dummy)) +
    geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
    geom_line() +
    facet_wrap(~ country)
@

<<>>=
# Calculate the joint standard error of the different
  se_data <-
    reduced_data %>%
    select(country, escs_dummy, wave, s.e.) %>%
    spread(escs_dummy, s.e.) %>%
    transmute(country, wave,
              se_diff = sqrt(abs(`1`^2 - `0`^2)))

@

<<include = T, out.height = '5in', out.width = '5.5in', fig.align = 'center'>>=

# Calculate the different between the gap and together with it's joint s.e graph
# the absolut difference.

countries <- c("Chile", "Austria", "Belgium", "Canada", "Czech Republic", "Denmark",
                 "Finland", "France", "Germany", "Italy", "Japan", "Netherlands", "Norway",
                 "Poland", "Spain", "Sweden", "United Kingdom", "United States")

reduced_data %>%
    select(country, escs_dummy, Mean, wave) %>%
    spread(key = escs_dummy, value = Mean) %>%
    mutate(diff = `1` - `0`) %>%
    gather(escs_dummy, Mean, -country, -wave, -`1`, -`0`) %>%
    left_join(se_data) %>%
    mutate(continent = countrycode(country, "country.name", "continent"),
           region = countrycode(country, "country.name", "region"),
           lower = Mean - 1.96 * se_diff,
           upper = Mean + 1.96 * se_diff) %>%
    filter(!is.na(continent), !is.na(region), country %in% countries) %>%
    ggplot(aes(as.factor(wave), Mean, group = country, colour = country)) +
    geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.1) +
    geom_line() +
    geom_point(size = 0.5) +
    scale_colour_discrete(guide = F) +
    # geom_smooth(aes(group = region), colour = "blue", method = "lm") +
    coord_cartesian(ylim = c(0, 4)) +
    facet_wrap(~ country) +
    ggtitle("math")

# Increase:  
# Sweden - steady increase in both tests
# Austria - increase in math - slight increase in read
# Finland - very sharp increase in both
# France - very sharp increase in both
# Netherlands - sharp increase in both

# Decrease:
# US - decrease in both tests
# Chile - decrease in both tests

# No change:
# Canada - stable red - increase math
# UK - slight decrease red - stable math
# Belgium - no change
# Czech republic - no change
# Denmark no change
# Germany - no change
# ITaly - no change
# Japan -  no change
# Norway - no change
# Poland - no change
# Spain - no change

@

<<>>=
# Next steps:

# Show country patterns with reading and math together into one graph

# Making country groups of the graphs showing that some countries are increasing, others are steady
# While others are decreasing. Do this with a few countries, but end by showing all countries.

# Continue by studying what's happening in those countries where it's increasing/decreasing
# In the gap graph

# Continue by doing the multilevel models to see what explains what. Include
# all indicators from the reardon/russian girl paper.

# Graph the increase in each country vs the increase/decrease of the economic inequality indicators
# Specially the 90/10

# Calculate how big is the gap between reading and math

# Continue with the PIRLS to see if there are specific patterns in 4th and 8th graders gap.

# Get each country trendline adjusted for the inequality indicators and place in the same country graph.

# Should I add the parent's education in the lm model to see how trends change adjusted for that?

# The gap between the top 90th and the 50th, did it grow?
# The gap between the top 50th and the 10th, did it grow?

# A weak welfare system, together with income inequality, what's their pattern?
# What if we put the school differentiation/tracking aspect in? Are there country groups based on these
# patterns.

# Show that within top and bottom educated categories, there is reasonable variation of SES index (to justify that your approach of suing the top and bottom percentiles within each category is the right approach)

# In countries where there is high differentiation/tracking, is there a jump in the evolution of the gap between PIRLS/TIMSS and PISA?

@

>>>>

\documentclass[11pt, a4paper]{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\bibliographystyle{apalike}
\pagestyle{headings}

@@

\title{First paper - Draft}
\author{Jorge Cimentada}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\setlength{\parindent}{2em}
\setlength{\parskip}{1em}
\showboxdepth=5
\showboxbreadth=5

@@

@@

{\centering \includegraphics[width=5.5in,height=5in]{figure/graphin_differences-1}

}

{\centering \includegraphics[width=5.5in,height=5in]{figure/unnamed-chunk-2-1}

}
